### 2018-06-15 VV570/HW4/assignment.tex
add ex1-1

%----------------------------------------------------------------------------------------
%	PROBLEM 1
%----------------------------------------------------------------------------------------
\section{Legendre Polynomials}
	\begin{enumerate}
		\item

>>>>

%----------------------------------------------------------------------------------------
%	PROBLEM 1
%----------------------------------------------------------------------------------------
\section{Legendre Polynomials}
	\begin{enumerate}
		\item
			\begin{proof}
				Let
				\begin{equation}
					\varphi(x) = (x^2-1)^n
				\end{equation}
				then
				\begin{equation}
					Q_n(x) = \frac{1}{2^n n!}\varphi^{(n)}(x)
				\end{equation}
				and
				\begin{equation}
					\varphi^{(k)}(1) = \varphi^{(k)}(-1) = 0 \ \  (\text{$k=0,1, ... , n-1$})
				\end{equation}
				Suppose $h(x) \in C^n(-1,1)$, then performing integration by parts
				\begin{equation}
					\begin{aligned}
						\int_{-1}^{1} P_n(x)h(x)dx 
						& = \frac{1}{2^n n!}\int_{-1}^{1}\varphi^{(n)}(x)h(x)dx \\
						& = -\frac{1}{2^n n!} \int_{-1}^{1}\varphi^{(n-1)}(x)h'(x)dx \\
						& = ...\\
						& = \frac{(-1)^n}{2^n n!}\int_{-1}^{1}\varphi(x)h^{(n)}(x)dx
					\end{aligned}
				\end{equation}
				Thus, the proof can be discussed on 2 cases

				\begin{enumerate}
					\item 
						If the order of $g(x)$ is less than $n$, then 
						\begin{equation}
							g^{(n)}(x) = 0
						\end{equation}
						Thus
						\begin{equation}
							\int_{-1}^{1}Q_n(x)Q_m(x)dx = 0 \ \ (\text{$n\neq m$})
						\end{equation}

					\item
						If $g(x) = Q_n(x)$, the the $n-th$ derivative of $g(x)$ is
						\begin{equation}
							g^{(n)}(x) = Q^{(n)}(x) = \frac{(2n)!}{2^n n!}
						\end{equation} 
						Thus
						\begin{equation}
							\begin{aligned}
								\int_{-1}^{1}Q_n(x)Q_m(x)dx	
								& = \int_{-1}^{1}Q_n^2(x)dx \\
								& = \frac{(-1)^n (2n)!}{2^{2n}(n!)^2}\int_{-1}^{1}(x^2-1)^n dx\\
								& = \frac{(2n)!}{2^{2n}(n!)^2}\int_{-1}^{1}(1-x^2)^n dx\\
								& = \frac{(2n)!}{2^{2n}(n!)^2} \int_{0}^{\pi/2} cos^{2n+1}t dt\\
								& = \frac{(2n)!}{2^{2n}(n!)^2} \frac{2 \times 4 \times ... \times (2n)}{1\times3\times ... \times (2n+1)}\\
								& = \frac{2}{2n+1} \ \ (\text{$n = m$})
							\end{aligned}
						\end{equation}
				\end{enumerate}

				Thus, $(Q_n)_{n\in\mathbb{N}}$ are a sequence of orthogonal polynomials.

			\end{proof}
		\item
